---
title: "LAB9_AIRBNB"
author: "HOA TRAN "
date: "11/8/2021"
output:
  html_document:
    toc: true
    toc_float: true
    code_folding: hide
---

`````````{r setup, include=FALSE}
knitr::opts_chunk$set(
	echo = TRUE,
	message = FALSE,
	warning = FALSE
)
```


```{r}
setwd("C:/Users/Admin/Desktop/DA101/LABWORK/LAB_9")
Columbus_2021 <- read.csv("Columbus_2021_listings.csv")
library(ggplot2)
library(dplyr)
library(maps)
library(Hmisc)
library(ggthemes)
library(geosphere)
library(ggmap)
library(stringr)
library(GGally)
library (cowplot)

```

3. 
The potential stakeholders of my analysis are potential customers who want to rent an Airbnb or even potential people who want to become an Airbnb hosts. The repercussions of my analysis can be quite detrimental in statistical terms as well as communication ethic terms. That is to say that if my interpretations of the data is not carefully written or lack sufficient evidence, customers might be deter from using Airbnb services and this could bring a negative light on the potential usefulness of Airbnb. Moreover, falsely analyzing this data set can also hurt the business of many Airbnb hosts, meaning that I am, unethically, destroying their livelihood and also communicating to customers with false interpretations and/or misunderstood insight of the entire Airbnb service. Therefore, a careful and detailed analysis of this data set is highly needed as well as meaningful and concise conclusions and insights are also required to deliver an unbiased and thorough perspective of the Airbnb service so that customers and hosts can decide what and how they want to utilize the service of Airbnb. 

4. The predictors that can help to predict house prices that came to my mind when first thinking about this are : property_type, room_type,  neighbourhood_cleansed, reviews_per_month, beds, number_of_reviews, availability_60. The reason I chose them was because, based on my intuition, they could possibly contribute to the fluctuations of prices.

5.
```{r}
Columbus_2021 <- Columbus_2021 %>%
  	mutate(price = as.numeric(str_remove_all(price, "[$]")))
```

6.
```{r}

ggplot(Columbus_2021, aes(x=beds, y=price, color=room_type))+
  labs(X= "Number of beds", y="Price", title = "Housing Price of Airbnb by number of beds")+
  geom_point(alpha=0.5)+
  scale_y_log10() +
  geom_smooth(method=lm)+
   facet_wrap("room_type")+
  theme_classic()+
  theme(plot.title = element_text(hjust = 0.5)) 



  


```

```{r}
ggplot(Columbus_2021, aes(x=number_of_reviews, y= price, color=room_type))+
labs(x="Accommodates", y="Price", title = "Airbnb housing prices by accommodation")+
  facet_grid("room_type")+
  geom_jitter()+
    geom_smooth(method=lm)+
  theme(plot.title = element_text(hjust = 0.5)) +
  theme_clean()+
   theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))
```

```{r}
  ggplot(Columbus_2021, aes(x= room_type, y= price, fill=room_type))+
  labs(x="Property Types", y="Price", title="Airbnb housing prices by room type", )+
    geom_boxplot(width=0.5, notch=TRUE,outlier.colour="gray")+
      theme(plot.title = element_text(hjust = 0.5)) +
    theme(legend.key.height= unit(1, 'cm'),
        legend.key.width= unit(4, 'cm'))+
    theme(legend.text = element_text(size=10))+
    theme(legend.title = element_text(size=10))+
    theme(legend.position="right")+
    theme_clean()

  



```

7.
```{r}
Columbus =c(left=-83.2, bottom=39.8, right=-82.75, top=40.16)
columbus_map <- get_stamenmap(Columbus, zoom = 10, maptype ="terrain")

ggmap(columbus_map)+ 
  labs(x= "Longtitude", y="Latitude", title = "Airbnb locations in Columbus")+
geom_point(data = Columbus_2021, aes(x = longitude, y = latitude, color=room_type), 
        alpha=0.25)






```

8.
```{r}
longitude <- c(-82.9258, -82.9153, -83.0070, -83.0197,-82.998954 )
latitude  <- c(39.9658, 40.0505, 39.9598, 40.0017,39.961633 )
name <- c("Franklin Park Conservatory Garden", "Easton Town Center", "Center Of Science And Industry", "Ohio Stadium", "Ohio Statehouse")
landmarks <- data.frame(name, latitude, longitude) 


```

9.
```{r}

Columbus =c(left=-83.2, bottom=39.8, right=-82.75, top=40.16)
columbus_map <- get_stamenmap(Columbus, zoom = 10, maptype ="terrain")
map_1 <- ggmap(columbus_map)+ 
  labs(x="Longtitude", y="Latitude", title = "Airbnb locations in Columbus by prices")+
  geom_point(data = Columbus_2021, aes(x = longitude, y = latitude, color=price), alpha=0.5)+
  scale_colour_gradient(low = "blue",high = "red")+
  scale_size_continuous(range=c(4,12))
map_2 <- map_1+
  geom_point(data=landmarks, aes(x=longitude, y=latitude), pch=18, cex=5, col="yellow", bg="yellow", lwd=2)

map_2

```


10.
```{r}
Columbus_2021$dist_to_Franklin_Park =  distHaversine(Columbus_2021[c("longitude","latitude")], c (landmarks[1,2],landmarks[1,3])) 
Columbus_2021$dist_to_Easton_Town = distHaversine(Columbus_2021[c("longitude","latitude")], c (landmarks[2,2],landmarks[2,3]))
Columbus_2021$dist_to_Center_Science  = distHaversine(Columbus_2021[c("longitude","latitude")], c (landmarks[3,2],landmarks[3,3]))
Columbus_2021$dist_to_Ohio_Stadium  = distHaversine(Columbus_2021[c("longitude","latitude")], c (landmarks[4,2],landmarks[4,3]))
Columbus_2021$dist_to_Ohio_Statehouse  = distHaversine(Columbus_2021[c("longitude","latitude")], c (landmarks[5,2],landmarks[5,3]))


```


11.
```{r}
Columbus_2021 <- mutate( Columbus_2021, min_dist= apply(Columbus_2021[75:79], 1, FUN=min))
Columbus_2021 <- mutate (Columbus_2021,mean_dist= rowMeans(Columbus_2021 [75:79]))

```


12.
```{r}

ggplot(Columbus_2021, aes(x=accommodates,y=price  ))+
  labs(x=" Accomodates", y="Price", title="Airbnb housing prices by accommodation")+
  geom_jitter(color="red")+
   stat_smooth()+
  theme_clean()
priceregression<- lm(Columbus_2021$price ~ Columbus_2021$accommodates)
summary(priceregression)

  
```

The scatter plot shows that there seems to be a positive correlation (as there are more accommodates, prices increase) between the number of accommodations and the price of housing for Airbnb service. The relationship as mentioned is quite significant with lots of points clustered near the trend line around the 1-10 accommodates mark. However, as the trend line reaches 10 and above there are more outliers and the relationship seems to be not as strong compared to the previously mentioned one (since there are also less data points as there are more accommodates). 
The linear model regression between the price and accommodates variables shows that the intercept of the trend line is 35.5886, meaning that if there are no guests staying the price of housing will be 35.5886 dollars. Moreover, for each increase in accommodations (an increase by 1), the price of an Airbnb house will increase by 18.9836 dollars. The p-value for both the intercepts as well as the accommodates variables are smaller than 2e-16 (really close to 0), meaning that the accommodates variable is a reliable predictor for house pricing. Moreover, the Multiple R-squared is 0.4019 and Adjusted R-squared:  0.4015 which illustrates that the accommodates variable explains around 40% of the variances in the price variable (showing that the aforementioned predictor fits the model relatively well) and the high adjusted R-squared means that if we have additional input variables (to predict housing prices)are adding value to the model. In substantive significance terms, the accommodates variable is a pretty reliable predictor of housing prices and customers can observe the number of accommodations to have some ideas of how housing prices could change in the future. 


13.
```{r}

Columbus_2021_filtered <- filter(Columbus_2021, room_type=="Entire home/apt" | room_type=="Private room")
ggpairs(Columbus_2021_filtered, columns=c("availability_60",  "reviews_per_month", "beds", "accommodates", "room_type",  "number_of_reviews"))+
  theme_classic()


   

```
The graphics illustrates that the accommodates variable and the beds variable have a strong correlation with each other (their corr value being 0.875), meaning that by including them together in the model, this can negatively impact the accuracy of my model when trying to predict housing prices. The same case can also be seen for the number_of_reviews as well as reviews_per_month variable (with their correlations being 0.256) After seeing the graphic, I decide to exclude either the beds variable or accommodates variable when running a multiple linear regression to decide which predictor is the most accurate when predicting pricing for houses. Therefore, the variables that are good predictors and should be included in my models are number_of_reviews, beds and room_type based on the graphics showing the correlation among these variables and their graphics as shown above.


14.
```{r}
price_multiple_regression = lm(price~ room_type+beds+mean_dist+min_dist+number_of_reviews, data=Columbus_2021_filtered)
summary(price_multiple_regression)
```
The multiple linear regression of the predictors for price shows that the intercept is -3.708e+03, meaning that if everything else has a value of zero, the predicted price of housing will be -3.708e+03. Moreover, Private room (a category in the room_type variable) is a reliable predictor as evident in its low p-value (with its p-value being 4.89e-11 which is smaller than 0.05). As for the intercept of previously mentioned variable, we can see that if everything else is held constant, if the room being rented is a private room, it will decrease the predicted pricing by 36.93 dollars. The beds variable is also a reliable predictor (with its p-value being smaller than 0.05) and if everything else is held constant, each increase of one bed will increase the predicted price of housing by 29.63 dollars. The number_of_reviews variable is a good predictor for housing price due to the low p-value of 0.000204 (smaller than 0.05) and for each increase of one review, the predicted price of housing will decrease by 0.09865 dollars. As for the two distance variables, they are not good indicator for predicting housing prices due to their high p-values (higher than 0.05). The adjusted R-squared being 0.3829, means that the predictors can explain around 38.29% of the variance in the price variable, showing that the included predictors are not too well fit for the model. With all of that said, we can conclude that the private room variable, beds and number_of_reviews are reliable predictors for housing prices. 


15.
```{r}
ggplot(Columbus_2021_filtered,aes(x=price,y=rstandard(price_multiple_regression)))+
  geom_hline(yintercept=0)+
  geom_point()
```


For trying to test the assumption that the residuals are uncorrelated with mean 0 and constant variance and have no pattern, I tried to run the code chunk with the y value being rstandard(price_multiple_regression)  but an error appeared saying Aesthetics must be either length 1 or the same as the data (1344): y 

```{r}
hist(price_multiple_regression$resid, breaks=50)
```


```{r}
qqnorm(price_multiple_regression$resid)
qqline(price_multiple_regression$resid)
```

The given histogram illustrates that the residuals of the regression model is normally distributed (as evident in the bell-shaped of the histogram). The Q-Q plot shows that the data points are more skewed to the right from -3 to -2 and are relatively straight from -2 to 1. Moreover, a significant feature can be seen is that from 2 to 3 the data points are more skewed to the left with lots of outliers points being far away from the line. Also, the line is not a straight line but it more skewed to the right. All of this means that the residuals are normally distributed as proven by the above histogram. With all of that in mind, we can conclude that the residuals are normally distributed.


16.
Based on the regression models and the validation of said model, in terms of statistical significance, if everything else is held constant, private room will decrease the price by 36.93 dollars, an increase of 1 bed will increase the predicted price by 29.63 dollars, the mean_dist will increase the predicted price (by 0.9558 dollars) and the min_dist variable will decrease the predicted price  (by 0.9557 dollars) for each additional increase of 1 unit of measurement. Also, the number_of_reviews variable will decrease the price by 0.9865 dollars for each additional review. By observing the R-squared value (multiple adjusted R-squared being around 0.4), it is clear to conclude that the model was relatively decent in terms of how well fit it, meaning that the model was, in fact, of some significance and can be used to predict the price of housing. 


17.
```{r}
library(MASS)


stepPredictors = Columbus_2021_filtered[complete.cases(Columbus_2021_filtered[,c("price","room_type","beds")]),]
step_forward = stepAIC(lm(price~1, data = stepPredictors),
                       scope=~.+room_type + beds + min_dist + mean_dist, distance = "forward")
step_forward$anova

```


```{r}
step_backward = stepAIC(lm(price~room_type + beds + min_dist + mean_dist, data=stepPredictors , distance = "backward"))
step_backward$anova
```
The two stepwise model predictions show that all 4 variables: min_dist, mean_dist, room_type and beds are good  predictors for housing prices with room_type and beds being the most reliable one among the four. Therefore, when trying to predict the changes in housing price, one could based on the two aforementioned variables to make assumptions about such subject matter. As for the predictor I would choose, I would go with room_type, beds and either one of the two min_dist or mean_dist since they have an equal AIC value (as shown in the two stepwise models above).


18.
```{r}
 modelname = lm(price ~ room_type + beds + property_type, data=Columbus_2021)
lowprice <- data.frame(room_type="Shared room", beds= 2, property_type="Shared room in hostel")
predict(modelname, lowprice)
middleprice <- data.frame(room_type="Private room", beds= 4,property_type="Private room in rental unit")
predict(modelname, middleprice)
highprice <- data.frame(room_type="Entire home/apt", beds= 10,property_type="Entire residential home")
predict(modelname, highprice)

```

19. 
Based on my analysis, the characteristics of renting a house with high price in Columbus are that when renting, an option of renting an entire home or apartment with lots of bedrooms or beds (for my analysis above, i decided to choose 10 beds as a prediction) and the rented place could also be a guesthouse, a condominium or a residential home. The final model above illustrates that the types of room and the number of beds are reliable predictors for housing prices and the addition of property_type is also a good contributing factor to decide the price of housing in Columbus. That is to say that renting entire home and apartments cost much more compared to the other ones and the types of property such as residential home and so on are indicative of high prices. Moreover, the increase number of beds are also pointing to higher prices. With that said, there are pitfalls in my analysis as it failed to include all of the landmarks or places of popular attractions in Columbus since these places have high number of people visiting, meaning that there might be more potential customers. If my analysis was able to do so, a bigger picture of how distances to those places could affect prices would be more clear. Another noticeable flaw is that my analysis doesn't include every potential predictors in this broad data set given the limitations of my current skill-sets in data analytics, so when one is examining my report, he or she should proceed with the knowledge that the analysis is made by an inexperienced person and the chosen predictors aren't the best at predicting house prices as they are only used to help customers, to a certain extent, know about future prices. Therefore, when examining an analysis, the credibility of the analysts and the information given must be proceeded with caution as not everything is absolutely correct and predictors are only used to help people to know the trend of prices to a certain extent because they are purely based on statistical significance, but in reality, there are other factors that can contribute to fluctuating prices. Therefore, when interpreting data, one should also know about the statistical significance and differentiate it from substantive significance. 

20.
The article discusses about the challenges for Airbnb given the context of the Covid pandemic and other pressing concerns in society.Given my analysis, it is not sufficient to predict the entire future of the Airbnb industry as the given predictors are only used to predict a certain trend in statistical significance and do not include in factors such as social biases, racism and others with similar characteristics. In order to understand fully how prices might fluctuate in the future, as said in the article, one must consider many factors and how they exert their influences on society and customers as a whole. By doing so, a more comprehensive of the state of housing prices can be seen rather than just basing solely on my analysis, showing that data analysis can only do so much and a deeper social understanding is required to fully comprehending certain problems. 





